\documentclass[]{twentysecondcv}

\begin{document}

%%%%%%%%%%%%%%%%%
%%PROFILE SIDE BAR%%
%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%
%%PERSONAL INFO%%%
%%%%%%%%%%%%%%%%

\cvname{Rubén Hernández} %your name
\cvjobtitle{Software Engineer}%your actual job position
\cvdate{May 19}%date of birth
\cvaddress{Mexico}%address
\cvnumberphone{+52 81 8088 5799}%telphone number
\cvmail{rahernandezgon@gmail.com}%e-mail
\cvsite{https://www.linkedin.com
/in/RubenHernandezGon}%personal site


\aboutme{

I like reaching new solutions by applying the knowledge and skills I acquired during the research I have done previously. Marketability and user satisfaction are the areas I would love to keep improving in the projects I work on.}%About me section

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%Skill bar section, each skill must have a value between 0 an 6 (float)%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\skills{{Emotional Intelligence/4.8},{Creativity/4.4},{Analytic/4.2},{Written \& Oral Communication/3.2},{Conflict resolution skills/4}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%Skill bar section, each skill must have a value between 0 an 6 (float)%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\languages{{Spanish (Native)/5}, {English (IELTS 6.5)/4.5}, Japanese (Basic)/0.8}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%Skill text section, each skill must have a value between 0 an 6%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\skillstext{{Data Analysis/4},{Code Validation/5},{Working Remotely/8}}

\makeprofile
%%%%%%%%%%%%%%%%%%%%
%%END PROFILE SIDE BAR%%
%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%
%%%%%%%%BODY%%%%%%%%
%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%
%%SIMPLE SECTION%%%%%%
%%%%%%%%%%%%%%%%%%%%
\section{Interests}
Improving user satisfaction and ease of use in the projects I work on. Creating resilient interfaces providing comfortable user  experiences. I like to indulge in game design and cocktail brewing as hobbies.

\section{Education}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%TWENTY LIST ITEMS%%%%%%%%%%%%%%
%%    Four arguments: date; title; where; description %%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{twenty}
  \twentyitem
    {2010-2017}
    {Bachelor's Degree {\normalfont in Computer Science}}
    {Monterrey, N.L, Mexico}
    {\emph{Instituto Tecnológico y de Estudios Superiores de Monterrey}}
\end{twenty}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%TWENTY LIST SHORTITEMS%%%%%%%%%%%%%%
%%% Two arguments: date; title/description %%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Work Experience}

\begin{twenty}
  \twentyitem
    {2018-2020}
    {Logic Information Systems | Support Team}
    {Support Consultant}
    {Provided thorough IT support and services to whom we have installed Oracle Retail Merchandising Systems. I specialized to meet our client's needs related to database, server and script related issues, and developed additional functionalities for their retail systems according to their requests.}
\end{twenty}




\section{Achievements}

\begin{twenty}
  \twentyitem
    {2018}
    {Logic Information Systems}
    {Support Consultant}
    {Initiated the support team in Logic Information Systems’ Mexico Branch and was responsible to provide support to our most active client" to "Was responsible to provide support to our most active client.}
  \twentyitem
    {2018}
    {Logic Information Systems}
    {Support Consultant}
    {Fixed an issue in our client’s system in which there was duplicate data being created.}
\twentyitem
    {2020}
    {Logic Information Systems}
    {Support Consultant}
    {Developed a custom functionality that would help our client’s system to recover lost prices before they are applied in their respective stores. This was a temporary fix that would prevent losing sales in our stores by applying incorrect prices while the root cause was fixed.}
\twentyitem
    {2016}
    {Cintermex}
    {Web Developer}
    {Redesigned an existing website implementing user sessions, allowing them to consult their remaining debts with our client. This project was developed using Javascript, HTML and implementing the Django to upgrade the past design.}
\twentyitem
    {2016}
    {Instituto Tecnológico y de Estudios Superiores de Monterrey}
    {Computer Science Student}
    {Designed a graphic input interface ran with Blockly blocks representing the code of our compiler's language. This project was developed utilizing Python in our compiler and Javascript in our graphic interface.}
\end{twenty}

\section{Computer Skills}

\begin{twentyshort}
  \twentyitemshort
    {Basic}
    {   JavaScript | Django | Unity | Bootstrap}
  \twentyitemshort
    {Intermediate}
    {   Python | C | C\# | C++ | Unix Servers | Ubuntu}
  \twentyitemshort
    {Advanced}
    {   Java | SQL | Oracle Retail Systems}
  \twentyitemshort
    {Expert}
    {   Windows}
\end{twentyshort}


%%%%%%%%%%%%%%%%%%%%
%%%%%ENDBODY%%%%%%%%
%%%%%%%%%%%%%%%%%%%%

\end{document} 